Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/ClementiBarba2020.tex
add details of Zenodo archives

%%%% Subject entries to be placed here %%%%
\subject{validation and verification, reproducibility and replication, computational modeling, computational physics, research software}

@@

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    related. This paper presents validation and replication studies in 
    electromagnetic excitations on nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software PyGBe: a boundary element
    solver with trecode acceleration and GPU capability.
    We replicate a result by Rockstuhl et al. (2005, doi:10/dsxw9d) with a
    two-dimensional boundary element method on silicon carbide particles,
    despite differences in our method. 
    The second replication case from Ellis et al. (2016, doi:10/f83zcb) looks
    at aspect ratio effects on high-order modes of localized surface phonon-polariton
    nanostructures. The results partially replicate: the wavenumber
    position of some mode match, but for other modes they differ.
    With virtually no information about the original simulations, 
    explaining the discrepancies is not possible. 
    A comparison with experiments that measured polarized reflectance 
    of silicon carbide nano pillars provides a validation case.
    The wavenumber of the dominant mode and two more do match, but 
    differences remain in other minor modes. 
    Results in this paper were produced with strict reproducibility
    practices, and we share reproducibility packages for all, including
    input files, execution scripts, secondary data, post-processing code and
    plotting scripts, and the figures (deposited in Figshare and Zenodo).
    In view of the many challenges faced, we propose that reproducible
    practices make replication and validation more feasible.

>>>>

%%%% Subject entries to be placed here %%%%
\subject{computer modeling and simulation, computational physics}

@@

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    related. This paper presents validation and replication studies in 
    electromagnetic excitations on nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software PyGBe: a boundary element
    solver with trecode acceleration and GPU capability.
    We replicate a result by Rockstuhl et al. (2005, doi:10/dsxw9d) with a
    two-dimensional boundary element method on silicon carbide particles,
    despite differences in our method. 
    The second replication case from Ellis et al. (2016, doi:10/f83zcb) looks
    at aspect ratio effects on high-order modes of localized surface phonon-polariton
    nanostructures. The results partially replicate: the wavenumber
    position of some mode match, but for other modes they differ.
    With virtually no information about the original simulations, 
    explaining the discrepancies is not possible. 
    A comparison with experiments that measured polarized reflectance 
    of silicon carbide nano pillars provides a validation case.
    The wavenumber of the dominant mode and two more do match, but 
    differences remain in other minor modes. 
    Results in this paper were produced with strict reproducibility
    practices, and we share reproducibility packages for all, including
    input files, execution scripts, secondary data, post-processing code and
    plotting scripts, and the figures (deposited in Zenodo).
    In view of the many challenges faced, we propose that reproducible
    practices make replication and validation more feasible.

### 2020-07-27 tex/results.tex
add details of Zenodo archives

Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short, and we have been doing this for many years and improving the process iteratively. 
The basic steps were already contained in the ``Reproducibility PI Manifesto'' of 2012 \cite{barba2012manifesto}, where Barba pledged to always share a manuscript's data, plotting scripts and figures under CC-BY (Creative Commons Attribution license).
Notably, this makes the figures re-usable by readers, without requiring them to ask permissions from the publisher, even if there was a transfer of copyright of the paper (the figures are included in the paper under the conditions of the public license). 
We later extended the practice to include all other digital artifacts associated with the results, beyond secondary data and figures. 
As in our previous papers, readers can reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Figshare and Zenodo. 
They include Jupyter notebooks with all the plotting code, and also the manually digitized data from the figures in the source articles for our replication cases.
Barba and Thiruvathukal, 2017 \cite{BarbaThiruvathukal2017}, explain that it is \emph{not enough} to provide these materials in a GitHub repository (the owner of a repository is always able to delete it), and one should deposit the reproducibility packages in an archival service providing a global identifier and permanent link (like a digital object identifier, DOI).
%[LIST, EXPLAIN, CITE ARCHIVES] 
The repository for this paper is at \url{https://github.com/barbagroup/pygbe_validation_paper}, which also includes the manuscript source files in LaTeX.
The software repository for \pygbe is at \url{https://github.com/barbagroup/pygbe}.

>>>>

Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short, and we have been doing this for many years and improving the process iteratively. 
The basic steps were already contained in the ``Reproducibility PI Manifesto'' of 2012 \cite{barba2012manifesto}, where Barba pledged to always share a manuscript's data, plotting scripts and figures under CC-BY (Creative Commons Attribution license).
Notably, this makes the figures re-usable by readers, without requiring them to ask permissions from the publisher, even if there was a transfer of copyright of the paper (the figures are included in the paper under the conditions of the public license). 
We later extended the practice to include all other digital artifacts associated with the results, beyond secondary data and figures. 
As in our previous papers, readers can reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Zenodo. 
They include Jupyter notebooks with all the plotting code, and also the manually digitized data from the figures in the source articles for our replication cases.
Barba and Thiruvathukal, 2017 \cite{BarbaThiruvathukal2017}, explain that it is \emph{not enough} to provide these materials in a GitHub repository (the owner of a repository is always able to delete it), and one should deposit the reproducibility packages in an archival service providing a global identifier and permanent link (like a digital object identifier, DOI).
%[LIST, EXPLAIN, CITE ARCHIVES]

The following items of archived digital artifacts accompany this paper:

\begin{compactitem}

\item[$\triangleright$] The software repository for \pygbe is at \href{https://github.com/barbagroup/pygbe}{https://github.com/barbagroup/pygbe}.

\item[$\triangleright$] The repository for this paper is at \href{https://github.com/barbagroup/pygbe_validation_paper}{https://github.com/barbagroup/pygbe\_validation\_paper}, which also includes the manuscript source files in LaTeX.

\item[$\triangleright$] The problem datasets for replication of Rockstuhl et al., 2005, are in the manuscript repository, but also archived in Zenodo  at \href{https://doi.org/10.5281/zenodo.3962534}{10.5281/zenodo.3962534}  \cite{ClementiBarba2020-Zen_a}.

\item[$\triangleright$] Execution files for all runs are archived in Zenodo at \href{https://doi.org/10.5281/zenodo.3962576}{10.5281/zenodo.3962576} \cite{ClementiBarba2020-Zen_b}.

\item[$\triangleright$] The problem datasets for validation and replication of results from Ellis et al., 2016 are archived in Zenodo at \href{https://doi.org/10.5281/zenodo.3962584}{10.5281/zenodo.3962584}\cite{ClementiBarba2020-Zen_c}.

\item[$\triangleright$] The file sets for reproducing the figures for the replication of results from Rockstuhl et al., 2005 are archived in Zenodo at \href{https://doi.org/10.5281/zenodo. 3962791}{10.5281/zenodo. 3962791} \cite{ClementiBarba2020-Zen_d}.

\item[$\triangleright$] The file sets for reproducing the figures for the validation and replication of results from Ellis et al., 2017 are arhived in Zenodo at \href{https://doi.org/3962797/zenodo.3962791}{10.5281/zenodo.3962797} \cite{ClementiBarba2020-Zen_e}.

\end{compactitem}
